This chapter provides information on the technical knowledge used in developing the mathematical model.
The chapter is divided according to the topics whose review and analysis were needed
to correctly model the physical phenomena occurring in the model.

\section{Meteorology}

\subsection{Unified Model}

\subsection{COAMPS Model}

\subsection{Weather Research and Forecasting Model}

\subsection{DB Model}

TODO



\section{Power Engineering}

[CITATIONS TODO]

Theoretical knowledge regarding the power engineering was required to correctly
analyze the energy system that was under this study. The most important 
characteristic of the renewable energy sources, is that they are different
from conventional ones, in the predictability 
of the power output. Most of the conventional energy sources are able to dynamically 
change the energy output by providing more fuel - or to be more strict - primary energy.
In the case of RES, most of the sources are not possible to control by a human.

The sun is the indirect source of all of the renewable energy sources - including wind, water, biomass
and biofuels. In this chapter there is a summary of all of the mentioned sources, that comes from sun, including
solar energy, which is acronym for direct use of solar energy as a primary energy.

\subsection{Conventional energy sources}

- introduction of conventional energy sources
- 

\subsection{Nuclear energy}

\subsection{Solar energy}

Solar energy is used in many different ways. It is possible to divide them by the energy conversion:

\begin{itemize}
    \item No conversion - lighting of rooms, passive heating,
    \item Photothermic conversion - water heating, air conditioning,
    \item Photoelectric conversion - electric energy,
    \item Photochemical conversion - photosynthesis, photography.
\end{itemize}

In case of analysis of the production of electricity, the photoelectric conversion is the most crucial one.
Photoelectric conversion uses photoelectric effect as a 

\subsection{Wind energy}

Wind energy is processed in a lot of different ways, and the 

\subsection{Biomass power}

\section{Scientific Computations}

Different types of Computations

\subsection{High Performance Computing}

Why HPC?

\subsection{Programming languages}

\section{Artificial Intelligence}

\subsection{Time-series modeling}

\subsection{Physics-informed neural networks}

